\subsection {Boolean Class and Objects}

Booleans are true and false values. There are only ever two boolean objects,
the true object and the false object.

\begin{lstlisting}
Object subClass: Boolean body: {
  class method true
  class method false
  method isTrue: block
  method isTrue: trueBlock else: falseBlock
  method isFalse: block
  method isFalse: falseBlock else: trueBlock
  method not
  method and: other
  method or: other
  method xor: other
  method asText
}
\end{lstlisting}

\subsubsection{Class Method true}
Returns the \textit{true} object.

\subsubsection{Class Method false}
Returns the \textit{false} object.

\subsubsection{Method isTrue:}
For the true object the method executes the \textit{block} parameter. For
the false object the method just returns.

\subsubsection{Method isTrue: else:}
For the true object the method executes the \textit{trueBlock} parameter.
For the false object the method executes the \textit{falseBlock} parameter.

\subsubsection{Method isFalse:}
For the false object the method executes the \textit{block} parameter. For
the true object the method just returns.

\subsubsection{Method isFalse: else:}
For the false object the method executes the \textit{trueBlock} parameter.
For the true object the method executes the \textit{falseBlock} parameter.

\subsubsection{Method not}
The method returns the inverse boolean object, for the true object the false
object is returned and for the false object the true object is returned.

\subsubsection{Method and:}
The method preforms the logical ``and'' operation between the \textit{self}
object and the \textit{other} parameter. The following table describes the
results for all the combinations.

\begin{center}
  \begin{tabular}{ | c | c | c | }
    \hline
    \textbf{self} & \textbf{other} & \textbf{result} \\ \hline
    true & true & true \\
    true & false & false \\
    false & true & false \\
    false & false & false \\ \hline
  \end{tabular}
\end{center}

\subsubsection{Method or:}
The method preforms the logical ``or'' operation between the \textit{self}
object and the \textit{other} parameter. The following table describes the
results for all the combinations.

\begin{center}
  \begin{tabular}{ | c | c | c | }
    \hline
    \textbf{self} & \textbf{other} & \textbf{result} \\ \hline
    true & true & true \\
    true & false & true \\
    false & true & true \\
    false & false & false \\ \hline
  \end{tabular}
\end{center}

\subsubsection{Method xor:}

\subsubsection{Method asText}
For the true object as Text object is returned with the value ``\textit{true}''
set. For the false object as Text object is returned with the value
``\textit{false}'' set.
